---
title: "Jonckheere Statistical Tests"
output: html_document
date: "2022-09-14"
---

```{r setup}
library(clinfun)
library(stringr)
```

The following code 

```{r Increasing_PyDi}
DATA_FOLDER <- "../Table_S2"
OUTPUT_FILE <- "../Table_S2/Table_S2_Jonckheere_Results.csv"
set.seed(0)
search_path <- paste(DATA_FOLDER, "/*For_Statistics.csv", sep='')
headers = paste("File", "Group", "P Value", sep=',')
write(headers, file = OUTPUT_FILE)
files <- Sys.glob(search_path)
for (i in files){
  print(i)
  data <- read.table(i, sep=',', header = TRUE)
  label_subgroups <- str_split(i, '_')
  n_subgroups <- length(label_subgroups[[1]])
  column_name = paste(label_subgroups[[1]][[n_subgroups - 5]],
                      label_subgroups[[1]][[n_subgroups - 4]],
                      sep='_')
  grp = label_subgroups[[1]][n_subgroups - 3]
  dimer = label_subgroups[[1]][n_subgroups -2]
  test_result <- jonckheere.test(data[[column_name]],
                                 data[["Count"]],
                                 alternative = "increasing",
                                 nperm = 100000)
  print(test_result)
  output <- paste(column_name,grp, dimer, test_result$p.value, sep=',')
  write(output, file = OUTPUT_FILE, append = TRUE)
}

```

  for (group in GROUPS){
      test_result <- jonckheere.test(data[[group]],
                                     data[["Effect_Group"]],
                                     alternative = "increasing",
                                     nperm = 1000)
      data_label <- regmatches(i, regexpr("E.*_by_.*",i))
      print(group)
      print(test_result)
      output <- paste(data_label, group, test_result$p.value, sep=',')
      write(output, file = OUTPUT_FILE, append = TRUE)
  }
```{r a}

#label_subgroups[[1]][[4]]
n_subgroups <- length(label_subgroups[[1]])
paste(label_subgroups[[1]][[n_subgroups - 3]], label_subgroups[[1]][[n_subgroups - 2]], sep='_')
```
The following code block performs the Jonckheere test for the data used in
table S5. 

```{r JT_Competition}
DATA_FOLDER <- "../Table_S5"
OUTPUT_FILE <- "../Table_S5/Jonckheere_Results.csv"
GROUPS <- list("ETS1_UV_r1", "ETS1_UV_r2", "ETS1_NUV_r1", "ETS1_NUV_r2")
set.seed(0)
search_path <- paste(DATA_FOLDER, "/*_by_*.csv", sep='')
headers = paste("File", "Group", "P Value", sep=',')
write(headers, file = OUTPUT_FILE)
files <- Sys.glob(search_path)
for (i in files){
  print(i)
  data <- read.table(i, sep=',', header = TRUE)
  for (group in GROUPS){
      test_result <- jonckheere.test(data[[group]],
                                     data[["Effect_Group"]],
                                     alternative = "increasing",
                                     nperm = 1000000)
      data_label <- regmatches(i, regexpr("E.*_by_.*",i))
      print(group)
      print(test_result)
      output <- paste(data_label, group, test_result$p.value, sep=',')
      write(output, file = OUTPUT_FILE, append = TRUE)
  }
}
```


```{r test}
ttable <- read.table("../Table_S5/ETS1_dimer_by_range.csv", sep=',', header=TRUE)
ttable
```


```{r indtest}
set.seed(0)
jonckheere.test(ttable[["ETS1_NUV_r1"]], ttable[["Effect_Group"]],alternative = "increasing",nperm = 1000)
```